\documentclass[a4paper, twoside, 12pt, noanswers]{exam}


% \documentclass[a4paper, 12pt, answers]{exam}
\usepackage{fontspec}

\usepackage{polyglossia}
\usepackage{dirtytalk}
\usepackage{enumitem}
\usepackage{fancybox}
\usepackage{multicol}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{enumerate}


\setdefaultlanguage{english} 


\setotherlanguage{hindi} 
\newfontfamily\devanagarifont[Script=Devanagari]{Shobhika} %fonts-> Shobhika, Mukta, Kalimati, Lohit Devanagari, Lohit Nepali
\defaultfontfeatures{Ligatures=TeX}

\newcommand{\textnp}{\texthindi}
\newenvironment{nepali}{\begin{hindi}}{\end{hindi}}
\newcommand{\cs}{C\texttt{\#}}


\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{multicol,adjustbox}

% \pointsinrightmargin %points in right margin
% \bracketedpoints

\nopointsinmargin %removes points from margin
\pointformat{} 

\unframedsolutions %do not show frame outside of solution


\CorrectChoiceEmphasis{\bfseries\boldmath} 
\renewcommand{\thepartno}{\alph{partno}} 
\renewcommand{\thesubpart}{(\roman{subpart})}
\renewcommand{\subpartlabel}{\thesubpart} 
\renewcommand{\choicelabel}{(\alph{choice})}

\thispagestyle{empty}

\cfoot[]{}
\clearpage

\begin{document}

%%%%%%Purbanchal University-2018%%%%%%
% 									 %															
%				2018				 %
%									 %
%%%%%%Purbanchal University-2018%%%%%%
\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2018/ \textnp{२०७५}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA454WN, Wireless Network and Mobile Computing (Elective-II) \hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				GROUP   A	
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}

	\question Explain in detail UMTS architecture, features and handover with neat sketch.
	\question Explain in detail about Ad-hoc networks and its routing strategies with neat sketch.
	\question Draw and explain the architecture of mobile computing and also discuss on the mobility management.

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%				GROUP   B					
	{\fullwidth{\centering \bfseries \underline{Group B}}\par}
	{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\question Describe the phases of HIPERLAN1.
	\question Explain the user scenarios of Bluetooth transmission.
	\question Discuss on any one type of encapsulation techniques used in mobile IP schemes.
\question Discuss on the features and services provided by GSM along with its security issues.
\question Explain IPV4. What are the advantages of IPV6 over IPV4?
\question What is mobile computing? Explain the transaction oriented TCP with an example.

\question Write short notes on any TWO:
	\begin{parts}
		\part DHCP
		\part Mobile Devices
		\part Infrared Vs Radio Transmission
	\end{parts}

\end{questions}
\newpage


%%%%%%Purbanchal University-2019%%%%%%
% 									 %															
%				2019				 %
%									 %
%%%%%%Purbanchal University-2019%%%%%%

\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2019/ \textnp{२०७६}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA454WN, Wireless Network and Mobile Computing (Elective-II) \hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
	\question Explain in detail about IEEE 802.11 protocol architecture,
	features and applications.

	\question Draw the basic architecture of GSM and explain in detail about
	its subsystems along with its interfaces.

	\question What is Mobile Computing? Draw and explain the architecture of
	mobile computing with various applications of it.


	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		{\fullwidth{\centering \bfseries \underline{Group B}}\par}
		{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\question  Describe the characteristics of an Ad-hoc networks..

	\question  What are the basic purposes of a DHCP? Explain.

	\question  Explain the features of tunneling and encapsulation.

	\question What is mobile TCP? Explain. Also point out demerits of
	conventional TCP incorporated in wireless environment.

	\question What is mobile IP? Describe the process of IP packet delivery with
	neat sketch.

	\question Explain the various generations of wireless networks with
	examples.

	\question  Write short notes on any TWO: 3+3
	\begin{parts}
		\part LTE and Bluetooth
		\part Mobility Management
		\part Handoff Process in GSM
	\end{parts}

\nomorequestions
\end{questions}

\end{document}